Concurrent Programming with CXL

### 2020-06-20 book/paper.tex
Working on exercises

\section*{Exercises}
\begin{enumerate}
\item Why do you suppose the code in Figure~\ref{fig:rwmulti} uses a flag
per process rather than a simple counter?
\item Can you write a version of this test that uses a counter instead
of a flag per process?
\item Write a ``library implementation'' of reader/writer locks so multiple
reader/writer locks can be instantiated.
\item Write a test program for ``bound locks'' (as implemented in the
exercises of the last chapter) that checks that up to \texttt{M} processes
can acquire the bound lock at the same time.
\end{enumerate}

@@

\begin{quote}
\begin{itemize}
\item Do you see what the problem is?
\item Does it depend on \texttt{N}, the number of philosophers?
\item Can you come up with a solution?
\item Does it matter in what order the philosophers lay down their forks?
\end{itemize}
\end{quote}

@@

\begin{quote}
\begin{itemize}
\item Try it out!
\end{itemize}
\end{quote}

>>>>

\section*{Exercises}
\begin{enumerate}
\item Why do you suppose the code in Figure~\ref{fig:rwmulti} uses a flag
per process rather than a simple counter?
Can you write a version of this test that uses a counter instead
of a flag per process?
% \item Write a ``library implementation'' of reader/writer locks so multiple
% reader/writer locks can be instantiated.
\item Write a test program for ``bound locks'' (as implemented in the
exercises of the last chapter) that checks that up to \texttt{M} processes
can acquire the bound lock at the same time.
\item Suppose a sports club has only one dressing room.  The policy is that
either only women or only men may be in the dressing room at any time.
Implement a ``dressing room lock'' that allows multiple people to enter the
dressing room while observing the policy.
\end{enumerate}

@@

\begin{quote}
\begin{itemize}
\item Do you see what the problem is?
\item Does it depend on \texttt{N}, the number of philosophers?
\end{itemize}
\end{quote}

@@

\section*{Exercises}
\begin{enumerate}
\item Does it matter in what order the philosophers lay down their forks?
\end{enumerate}
